Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-17 thesis/chapters/ch_introduction.tex
typo fix

While there is no real sharp transition where a galaxy is considered a ``dwarf" galaxy, historical definitions are based on luminosity, using the SMC and LMC as rough anchor points for the upper-end of the dwarf galaxy scale. \cite{Bullock2017} suggests a deliniation based on stellar mass. For this dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M_${\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.

>>>>

While there is no real sharp transition where a galaxy is considered a ``dwarf" galaxy, historical definitions are based on luminosity, using the SMC and LMC as rough anchor points for the upper-end of the dwarf galaxy scale. \cite{Bullock2017} suggests a deliniation based on stellar mass. For this dissertation, we follow this definition and consider galaxies with $M_* < 10^9$~M$_{\odot}$ as dwarf galaxies, and galaxies with $M_* < 10^5$~M$_{\odot}$ as UFDs.
